---
title: "EEG MRS"
author: "Shane McKeon"
date: "11/11/2021"
geometry: margin = 1in
output:
  pdf_document:  
    toc: true
    toc_depth: 4    
    fig_caption: yes
  latex_engine: xelatex

  html_document:
    df_print: paged
    code_folding: hide 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev='png', dpi=150, fig.width = 6, fig.height= 6, fig.align = 'center', fig.margin = TRUE, comment = NA)
```


```{r load-libraries, message=FALSE}
```


```{r, echo= FALSE, message = FALSE, warning = FALSE}

library(LNCDR)
library(data.table)
require(dplyr)
library(factoextra)
library(tidyverse)
require(knitr)
library(ggplot2)
library(e1071)
library(caret)
library(sjPlot)
library(directlabels)
library(tidyverse)
library(ggplot2)
library(readxl)
library(Hmisc)
library(lmerTest)
library(corrplot)
library(RColorBrewer)
library(data.table)
library(mediation)


```


# Behavior Across Age 

```{r, echo= FALSE, message = FALSE, warning = FALSE}
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/03.BehaviorAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)
agefile <- read.csv('H:/Projects/7TBrainMech/scripts/eeg/Shane/Results/Power_Analysis/Spectral_events_analysis/agefile_20220204.csv')
Behavior <- Behavior_Sublevel_Maria()
```

# Load MRS Regions
```{r, echo= FALSE, message = FALSE, warning = FALSE}
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/PrepMRSdata.R", envir = knitr::knit_global(), chdir = TRUE)
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)
MRS <- LoadMRS()

ROIs <- data.frame(MRS$roi, MRS$label)

ACC <- function() {
# ACC
roinumber = 7
z_thres = 2

ACC_Glu <- cleanGlutamate(MRS, roinumber)

ACC_Glu <- ACC_Glu %>%
  filter(GABA.SD <= 20, !is.na(GMrat)) %>% filter(roi == roinumber) %>%
  group_by(roi) %>%
  mutate(zscore_gaba=scale(GABA.Cr, center=T, scale=T)) %>%
  filter(abs(zscore_gaba) <= z_thres)

ACC_Glu_invage <- lm(data=ACC_Glu, Glu.Cr ~ invage + sex + GMrat)
#summary(ROI_Glu_invage)

var_Glu <- lm(Glu.Cr ~ invage + sex + GMrat, data=ACC_Glu, na.action=na.exclude)
ACC_Glu$Glu_ageResids <- (residuals(var_Glu))
ACC_Glu$Glu_ageResidsABS <- abs(residuals(var_Glu))

ACC_Glu$Subject <- ACC_Glu$ld8

ACC_Glu <- ACC_Glu %>% separate(ld8,c("luna","vdate"), remove=F)

# looking at GABA - Glu
ACC_Glu$zscoredGABAMinusGlu <- (ACC_Glu$zscore_gaba) - (ACC_Glu$zscore_glu)
ACC_Glu$zscoredGABAMinusGlu_abs <- abs(ACC_Glu$zscoredGABAMinusGlu)


}

RposteriorInsulta <- function() {

  roinumber = 3
  RPI_Glu <- cleanGlutamate(MRS, roinumber)
  
  RPI_Glu <- RPI_Glu %>%
    filter(GABA.SD <= 20, !is.na(GMrat)) %>% filter(roi == roinumber) %>%
    group_by(roi) %>%
    mutate(zscore_gaba=scale(GABA.Cr, center=T, scale=T)) %>%
    filter(abs(zscore_gaba) <= z_thres)
  
  RPI_Glu_invage <- lm(data=RPI_Glu, Glu.Cr ~ invage + sex + GMrat)
  #summary(ROI_Glu_invage)
  
  var_Glu <- lm(Glu.Cr ~ invage + sex + GMrat, data=RPI_Glu, na.action=na.exclude)
  RPI_Glu$Glu_ageResidsABS <- abs(residuals(var_Glu))
  RPI_Glu$Glu_ageResids <- (residuals(var_Glu))
  
  RPI_Glu$Subject <- RPI_Glu$ld8
  
  RPI_Glu <- RPI_Glu %>% separate(ld8,c("luna","vdate"), remove=F)
  
  # looking at GABA - Glu
  RPI_Glu$zscoredGABAMinusGlu <- (RPI_Glu$zscore_gaba) - (RPI_Glu$zscore_glu)
  RPI_Glu$zscoredGABAMinusGlu_abs <- abs(RPI_Glu$zscoredGABAMinusGlu)
  
}


LposteriorInsulta <- function() {
  
  roinumber = 4
  LPI_Glu <- cleanGlutamate(MRS, roinumber)
  
  LPI_Glu <- LPI_Glu %>%
    filter(GABA.SD <= 20, !is.na(GMrat)) %>% filter(roi == roinumber) %>%
    group_by(roi) %>%
    mutate(zscore_gaba=scale(GABA.Cr, center=T, scale=T)) %>%
    filter(abs(zscore_gaba) <= z_thres)
  
  LPI_Glu_invage <- lm(data=LPI_Glu, Glu.Cr ~ invage + sex + GMrat)
  #summary(ROI_Glu_invage)
  
  var_Glu <- lm(Glu.Cr ~ invage + sex + GMrat, data=LPI_Glu, na.action=na.exclude)
  LPI_Glu$Glu_ageResids <- (residuals(var_Glu))
  LPI_Glu$Glu_ageResidsABS <- abs(residuals(var_Glu))
  
  LPI_Glu$Subject <- LPI_Glu$ld8
  
  LPI_Glu <- LPI_Glu %>% separate(ld8,c("luna","vdate"), remove=F)
  
  # looking at GABA - Glu
  LPI_Glu$zscoredGABAMinusGlu <- (LPI_Glu$zscore_gaba) - (LPI_Glu$zscore_glu)
  LPI_Glu$zscoredGABAMinusGlu_abs <- abs(LPI_Glu$zscoredGABAMinusGlu)
  

}


MPFC <- function() {
  
roinumber = 8
MPFC_Glu <- cleanGlutamate(MRS, roinumber)

MPFC_Glu <- MPFC_Glu %>%
  filter(GABA.SD <= 20, !is.na(GMrat)) %>% filter(roi == roinumber) %>%
  group_by(roi) %>%
  mutate(zscore_gaba=scale(GABA.Cr, center=T, scale=T)) %>%
  filter(abs(zscore_gaba) <= z_thres)

MPFC_Glu_invage <- lm(data=MPFC_Glu, Glu.Cr ~ invage + sex + GMrat)
#summary(ROI_Glu_invage)

var_Glu <- lm(Glu.Cr ~ invage + sex + GMrat, data=MPFC_Glu, na.action=na.exclude)
MPFC_Glu$Glu_ageResidsABS <- abs(residuals(var_Glu))
MPFC_Glu$Glu_ageResids <- (residuals(var_Glu))

MPFC_Glu$Subject <- MPFC_Glu$ld8

MPFC_Glu <- MPFC_Glu %>% separate(ld8,c("luna","vdate"), remove=F)

MPFC_Glu$zscoredGABAMinusGlu <- (MPFC_Glu$zscore_gaba) - (MPFC_Glu$zscore_glu)
MPFC_Glu$zscoredGABAMinusGlu_abs <- abs(MPFC_Glu$zscoredGABAMinusGlu)



}

rightDLPFC <- function() {

roinumber = 9
z_thres = 2
RDLPFC <- cleanGlutamate(MRS, roinumber)

RDLPFC <- RDLPFC %>%
  filter(GABA.SD <= 20, !is.na(GMrat)) %>% filter(roi == roinumber) %>%
  group_by(roi) %>%
  mutate(zscore_gaba=scale(GABA.Cr, center=T, scale=T)) %>%
  filter(abs(zscore_gaba) <= z_thres)


RDLPFC_invage <- lm(data=RDLPFC, Glu.Cr ~ invage + sex + GMrat)
#summary(ROI_Glu_invage)

var_Glu <- lm(Glu.Cr ~ invage + sex + GMrat, data=RDLPFC, na.action=na.exclude)

RDLPFC$Glu_ageResidsABS <- abs(residuals(var_Glu))
RDLPFC$Glu_ageResids <- (residuals(var_Glu))

RDLPFC$Subject <- RDLPFC$ld8

RDLPFC<- RDLPFC %>% separate(Subject,c("luna","vdate"), remove=F)

#GABA - Glu vs age

RDLPFC$zscoredGABAMinusGlu <- RDLPFC$zscore_gaba - RDLPFC$zscore_glu

RDLPFC$zscoredGABAMinusGlu_abs <- abs(RDLPFC$zscoredGABAMinusGlu)




}

leftDLPFC <- function() {
  
roinumber = 10
LDLPFC <- cleanGlutamate(MRS, roinumber)

LDLPFC <- LDLPFC %>%
  filter(GABA.SD <= 20, !is.na(GMrat)) %>% filter(roi == roinumber) %>%
  group_by(roi) %>%
  mutate(zscore_gaba=scale(GABA.Cr, center=T, scale=T)) %>%
  filter(abs(zscore_gaba) <= z_thres)

LDLPFC_invage <- lm(data=LDLPFC, Glu.Cr ~ invage + sex + GMrat)
#summary(ROI_Glu_invage)

var_Glu <- lm(Glu.Cr ~ invage + sex + GMrat, data=LDLPFC, na.action=na.exclude)

LDLPFC$Glu_ageResidsABS <- abs(residuals(var_Glu))
LDLPFC$Glu_ageResids <- (residuals(var_Glu))

LDLPFC$Subject <- LDLPFC$ld8

# GABA - Glu 
LDLPFC$zscoredGABAMinusGlu<- LDLPFC$zscore_gaba - LDLPFC$zscore_glu
LDLPFC$zscoredGABAMinusGlu_abs <- abs(LDLPFC$zscoredGABAMinusGlu)

LDLPFC<- LDLPFC %>% separate(Subject,c("luna","vdate"), remove=F)


}

vars <- c("Subject", "luna", "label", "age", "Glu.Cr", "GABA.Cr", "zscore_glu", "zscore_gaba", "Glu_ageResids", "Glu_ageResidsABS", "zscoredGABAMinusGlu", "zscoredGABAMinusGlu_abs")
  ACCdf <- ACC_Glu[vars]
  MPFCdf <- MPFC_Glu[vars]
  RDLPFCdf <- RDLPFC[vars]
  LDLPFCdf <- LDLPFC[vars]
  RPIdf <- RPI_Glu[vars]
  LPIdf <- LPI_Glu[vars]
  

allMRSregions <- rbind(ACCdf, MPFCdf) %>% rbind(., RDLPFCdf) %>% rbind(., LDLPFCdf) %>% rbind(., RPIdf) %>% rbind(., LPIdf)

```

# Delay 
```{r, echo= FALSE, message = FALSE, warning = FALSE}
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/02.FrequencyAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)

delayOnly <- DelayOnly_Sublevel_3_4()
delayOnly_TrialLevel <- Only_Take_One_Delay_Bin_TrialLevel()
delayOnly_TrialLevel_gamma <- delayOnly_TrialLevel$allGamma
delayOnly_SubLevel <- delayOnly$alldata_delayOnly

gammavars <- grep("Gamma",names(delayOnly_SubLevel),value=TRUE)
allGamma <- delayOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",gammavars)]
colnames(allGamma) <-  sub("Gamma.", "", colnames(allGamma))
allGamma$Band <- "Gamma"

allGamma$epoch <- "Delay"
allGamma$Region <- "Whole Brain"


### Regional Data 
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/02.FrequencyAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)

delayRegions3_4 <- RegionstoSpectralEventData_SubjectLevel()

gammavars <- grep("Gamma",names(delayRegions3_4),value=TRUE)
allGamma <- delayRegions3_4[,c("Subject", "inverseAge","age", "Group",gammavars)]
colnames(allGamma) <-  sub("Gamma.", "", colnames(allGamma))
allGamma$Band <- "Gamma"

WBgammavars <- grep("Gamma",names(delayOnly_SubLevel),value=TRUE)
WBallGamma <- delayOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",WBgammavars)]
colnames(WBallGamma) <-  sub("Gamma.", "", colnames(WBallGamma))
colnames(WBallGamma) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(WBallGamma))
colnames(WBallGamma) <-  sub("_sd", "_Variability", colnames(WBallGamma))
WBallGamma$Region <- "Whole Brain"
WBallGamma$epoch <- "Delay"
WBallGamma$Band <- "Gamma"

selectiveFrontalVars <-  grep("selectiveFrontal",names(allGamma),value=TRUE)
allselectiveFrontal3_4 <- allGamma[,c("Subject", "inverseAge","age", "Band", "Group",selectiveFrontalVars)]
colnames(allselectiveFrontal3_4) <-  sub("_selectiveFrontal", "", colnames(allselectiveFrontal3_4))
colnames(allselectiveFrontal3_4) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(allselectiveFrontal3_4))
colnames(allselectiveFrontal3_4) <-  sub("_sd", "_Variability", colnames(allselectiveFrontal3_4))
allselectiveFrontal3_4$Region <- "SelectiveFrontal"
allselectiveFrontal3_4$epoch <- "Delay"

# Frontal
FrontalVars <-  grep("_Frontal",names(allGamma),value=TRUE)
allFrontal3_4 <- allGamma[,c("Subject", "inverseAge","age", "Band", "Group",FrontalVars)]
colnames(allFrontal3_4) <-  sub("_Frontal", "", colnames(allFrontal3_4))
colnames(allFrontal3_4) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(allFrontal3_4))
colnames(allFrontal3_4) <-  sub("_sd", "_Variability", colnames(allFrontal3_4))
allFrontal3_4$Region <- "Frontal"
allFrontal3_4$epoch <- "Delay"

# occipital
Occipitalvars <-  grep("Occipital",names(allGamma),value=TRUE)
allOccipital3_4 <- allGamma[,c("Subject", "inverseAge","age", "Band", "Group",Occipitalvars)]
colnames(allOccipital3_4) <-  sub("_Occipital", "", colnames(allOccipital3_4))
colnames(allOccipital3_4) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(allOccipital3_4))
colnames(allOccipital3_4) <-  sub("_sd", "_Variability", colnames(allOccipital3_4))
allOccipital3_4$Region <- "Occipital"
allOccipital3_4$epoch <- "Delay"


# parietal 
Parietalvars <-  grep("Parietal",names(allGamma),value=TRUE)
allParietal3_4 <- allGamma[,c("Subject", "inverseAge","age", "Band", "Group",Parietalvars)]
colnames(allParietal3_4) <-  sub("_Parietal", "", colnames(allParietal3_4))
colnames(allParietal3_4) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(allParietal3_4))
colnames(allParietal3_4) <-  sub("_sd", "_Variability", colnames(allParietal3_4))
allParietal3_4$Region <- "Parietal"
allParietal3_4$epoch <- "Delay"


# dlpfc 
dlpfcvars <-  grep("dlpfc",names(allGamma),value=TRUE)
alldlpfc3_4 <- allGamma[,c("Subject", "inverseAge","age", "Band", "Group",dlpfcvars)]
colnames(alldlpfc3_4) <-  sub("_dlpfc", "", colnames(alldlpfc3_4))
colnames(alldlpfc3_4) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(alldlpfc3_4))
colnames(alldlpfc3_4) <-  sub("_sd", "_Variability", colnames(alldlpfc3_4))
alldlpfc3_4$Region <- "DLPFC"
alldlpfc3_4$epoch <- "Delay"

# combine all regions 
allRegions3_4 <- rbind(allselectiveFrontal3_4, allOccipital3_4) %>% rbind(., allParietal3_4)%>% rbind(.,alldlpfc3_4)%>% rbind(.,allFrontal3_4) %>% rbind(., WBallGamma)

```


# Fix
```{r, echo= FALSE, message = FALSE, warning = FALSE}

FixOnly <- FixOnly_Sublevel()
FixOnly_SubLevel <- FixOnly$alldata_FixOnly

gammavars <- grep("Gamma",names(FixOnly_SubLevel),value=TRUE)
allGammaFix <- FixOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",gammavars)]
colnames(allGammaFix) <-  sub("Gamma.", "", colnames(allGammaFix))
allGammaFix$Band <- "Gamma"

allGammaFix$epoch <- "Fix"
allGammaFix$Region <- "Whole Brain"


### Regional Data
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/02.FrequencyAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)

fixRegions_fix <- RegionstoSpectralEventData_SubjectLevel_fix()


gammavars <- grep("Gamma",names(fixRegions_fix),value=TRUE)
allGamma <- fixRegions_fix[,c("Subject", "inverseAge", "age", "Group",gammavars)]
colnames(allGamma) <-  sub("Gamma.", "", colnames(allGamma))
allGamma$Band <- "Gamma"

WBgammavars <- grep("Gamma",names(FixOnly_SubLevel),value=TRUE)
WBallGamma <- FixOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",WBgammavars)]
colnames(WBallGamma) <-  sub("Gamma.", "", colnames(WBallGamma))
colnames(WBallGamma) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(WBallGamma))
colnames(WBallGamma) <-  sub("_sd", "_Variability", colnames(WBallGamma))
WBallGamma$Region <- "Whole Brain"
WBallGamma$epoch <- "Fix"
WBallGamma$Band <- "Gamma"

# selective frontal
selectiveFrontalVars <-  grep("selectiveFrontal",names(allGamma),value=TRUE)
allselectiveFrontal_fix <- allGamma[,c("Subject", "inverseAge", "age", "Band","Group",selectiveFrontalVars)]
colnames(allselectiveFrontal_fix) <-  sub("_selectiveFrontal", "", colnames(allselectiveFrontal_fix))
colnames(allselectiveFrontal_fix) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(allselectiveFrontal_fix))
colnames(allselectiveFrontal_fix) <-  sub("_sd", "_Variability", colnames(allselectiveFrontal_fix))
allselectiveFrontal_fix$Region <- "SelectiveFrontal"
allselectiveFrontal_fix$epoch <- "Fix"

# frontal
FrontalVars <-  grep("_Frontal",names(allGamma),value=TRUE)
allFrontal_fix <- allGamma[,c("Subject", "inverseAge", "age", "Band","Group",FrontalVars)]
colnames(allFrontal_fix) <-  sub("_Frontal", "", colnames(allFrontal_fix))
colnames(allFrontal_fix) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(allFrontal_fix))
colnames(allFrontal_fix) <-  sub("_sd", "_Variability", colnames(allFrontal_fix))
allFrontal_fix$Region <- "Frontal"
allFrontal_fix$epoch <- "Fix"

# occipital
Occipitalvars <-  grep("Occipital",names(allGamma),value=TRUE)
allOccipital_fix <- allGamma[,c("Subject", "inverseAge", "age", "Band","Group",Occipitalvars)]
colnames(allOccipital_fix) <-  sub("_Occipital", "", colnames(allOccipital_fix))
colnames(allOccipital_fix) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(allOccipital_fix))
colnames(allOccipital_fix) <-  sub("_sd", "_Variability", colnames(allOccipital_fix))
allOccipital_fix$Region <- "Occipital"
allOccipital_fix$epoch <- "Fix"


# parietal 
Parietalvars <-  grep("Parietal",names(allGamma),value=TRUE)
allParietal_fix <- allGamma[,c("Subject", "inverseAge", "age", "Band","Group",Parietalvars)]
colnames(allParietal_fix) <-  sub("_Parietal", "", colnames(allParietal_fix))
colnames(allParietal_fix) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(allParietal_fix))
colnames(allParietal_fix) <-  sub("_sd", "_Variability", colnames(allParietal_fix))
allParietal_fix$Region <- "Parietal"
allParietal_fix$epoch <- "Fix"

# dlpfc 
dlpfcvars <-  grep("dlpfc",names(allGamma),value=TRUE)
alldlpfc_fix <- allGamma[,c("Subject", "inverseAge", "age", "Band","Group",dlpfcvars)]
colnames(alldlpfc_fix) <-  sub("_dlpfc", "", colnames(alldlpfc_fix))
colnames(alldlpfc_fix) <-  sub("log1p_Power", "log1p_Trial_Power", colnames(alldlpfc_fix))
colnames(alldlpfc_fix) <-  sub("_sd", "_Variability", colnames(alldlpfc_fix))
alldlpfc_fix$Region <- "DLPFC"
alldlpfc_fix$epoch <- "Fix"

# combine all regions 
allRegions_fix <- rbind(allselectiveFrontal_fix, allOccipital_fix) %>% rbind(., allParietal_fix) %>% rbind(.,alldlpfc_fix) %>% rbind(., allFrontal_fix) %>% rbind(., WBallGamma)

```
```

# Combine Delay, Fix, MRS, and Behavior
```{r, echo= FALSE, message = FALSE, warning = FALSE}

allepochs <- rbind(allRegions3_4, allRegions_fix )
allepochs <- allepochs %>% separate(Subject,c("luna","vdate"), remove=F)
 
EEGMRSBehavior <- merge(allepochs, Behavior, by = c("Subject", "inverseAge", "age"), all.x = T, all.y = T) %>% merge(., allMRSregions, by = "luna")

lunaize(ggplot(data = allepochs , 
               aes(x = age, y = log1p_Trial_Power, color = epoch)) +geom_point()
     + stat_smooth(method='gam', alpha=0.15) + facet_wrap( . ~ Region, ncol = 6))

lunaize(ggplot(data = EEGMRSBehavior %>% filter(., Region == 'DLPFC') %>% mutate(ageGroup = as.factor(ifelse(age.x <= 18, 'Adol', 'Adult'))), 
               aes(x = log1p_Trial_Power, y = zscoredGABAMinusGlu_abs, color = epoch)) 
     + stat_smooth(method='gam', alpha=0.15) + facet_wrap( . ~ label, ncol = 6))

gam.model <- gam(zscoredGABAMinusGlu_abs ~ s(Event_Number_Variability, k = 4 , by = as.factor(epoch)) +  s(age.x, k=4, by = as.factor(epoch)),
                 data = EEGMRSBehavior  %>% filter(label == 'MPFC') %>% mutate(ageGroup = as.factor(ifelse(age.x <= 18, 'Adol', 'Adult'))))
summary(gam.model)




# mediation 
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/06.Mediation.R", envir = knitr::knit_global(), chdir = TRUE)

other_vars <- c("log1p_Trial_Power","zscoredGABAMinusGlu_abs")

mediationAnalysis(EEGMRSBehavior %>% filter(label == 'MPFC') %>% filter(epoch == 'Delay'), other_vars)


```

