---
title: "SpectralEvents_PaperFigs"
author: "Shane McKeon"
date: "02/01/2022"
geometry: margin = 1in
output:
  pdf_document:  
    toc: true
    toc_dept/Volumes/Hera 4    
    fig_caption: yes
  latex_engine: xelatex

  html_document:
    df_print: paged
    code_folding: hide 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev='png', dpi=150, fig.width = 6, fig.height= 6, fig.align = 'center', fig.margin = TRUE, comment = NA)
```


```{r load-libraries, message=FALSE}
```


```{r, echo= FALSE, message = FALSE, warning = FALSE}

library(LNCDR)
library(data.table)
require(dplyr)
library(factoextra)
library(tidyverse)
require(knitr)
library(ggplot2)
library(e1071)
library(caret)
library(sjPlot)
library(directlabels)
attach(mtcars)
library(grid)
library(gridExtra)
library(cowplot)
library(plotrix)
library(mgcv)
library(plotly)

```

# Behavior Across Age 
## Best Saccade
```{r, echo= FALSE, message = FALSE, warning = FALSE}
sys.source("/Volumes/Hera/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)
sys.source("/Volumes/Hera/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/03.BehaviorAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)
agefile <- read.csv('/Volumes/Hera/Projects/7TBrainMech/scripts/eeg/Shane/agefile_20220204.csv')
Behavior <- Behavior_Sublevel_Maria()

Behavior <- Behavior %>% filter(visitno ==1)

BS <- bestSaccade(Behavior)

BSV <- bestSaccadeVariability(Behavior)

PE <- absPositionError(Behavior)

PEV <- absPositionErrorVariability(Behavior)

lat <- mgsLatency(Behavior)

latV <- mgsLatencyVariability(Behavior)

# combine all the p values so that we can correct them for multiple comparisons 
behaviorPvalues <- data.frame(BS$Pvalue[1], BSV$Pvalue[1], PE$Pvalue[1], PEV$Pvalue[1], lat$Pvalue[1], latV$Pvalue[1])

p.adjust((behaviorPvalues), method = "bonferroni")

cowplot::plot_grid(BS$BSgraph, lat$latgraph,BSV$BSVgraph,latV$latvgraph, labels = c('A','B','C','D'), label_size = 30, rel_widths = c(1,1.1))


# bar graphs
behaviorAge <- merge(Behavior, agefile, by = c("Subject", "age"))
groupBehaviorAge <- aggregate(.~ Group, behaviorAge[2:15], mean)
sderror<-std.error(groupBehaviorAge$mgsLatency_sd)

YMIN <- groupBehaviorAge$mgsLatency_sd-sderror

YMAX <- groupBehaviorAge$mgsLatency_sd+sderror

lunaize(ggplot(groupBehaviorAge, aes(x=Group, y=mgsLatency_sd, ymin= YMIN, ymax=YMAX , group = Group, fill = Group)) + geom_col(position = 'dodge') + geom_errorbar(position='dodge') )

behaviorAge %>% dplyr::filter(., Group == c(1,2)) %>% t.test(absBestError_sd ~ Group, data = .)

 #significant periods of growth
  gam.model <- gam(absBestError_sd ~ s(age), data = behaviorAge)
  gam.growthrate <- gam_growthrate(gam.model, agevar = 'age')
  gam_growthrate_plot(behaviorAge, gam.model, gam.growthrate, agevar = 'age', yvar = 'absBestError_sd', draw_points = F)

```

# Frequency Bands Across Age
## Delay Period
### Whole Brain 
```{r, echo= FALSE, message = FALSE, warning = FALSE}
sys.source("/Volumes/Hera/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)
sys.source("/Volumes/Hera/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/02.FrequencyAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)

delayOnly <- DelayOnly_Sublevel_3_4()
delayOnly_SubLevel <- delayOnly$alldata_delayOnly

alphavars <- grep("Alpha",names(delayOnly_SubLevel),value=TRUE)
allAlpha <- delayOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",alphavars)]
colnames(allAlpha) <-  sub("Alpha.", "", colnames(allAlpha))
allAlpha$Band <- "Alpha"


thetavars <- grep("Theta",names(delayOnly_SubLevel),value=TRUE)
allTheta <- delayOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",thetavars)]
colnames(allTheta) <-  sub("Theta.", "", colnames(allTheta))
allTheta$Band <- "Theta"

betavars <- grep("Beta",names(delayOnly_SubLevel),value=TRUE)
allBeta <- delayOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",betavars)]
colnames(allBeta) <-  sub("Beta.", "", colnames(allBeta))
allBeta$Band <- "Beta"


gammavars <- grep("Gamma",names(delayOnly_SubLevel),value=TRUE)
allGamma <- delayOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",gammavars)]
colnames(allGamma) <-  sub("Gamma.", "", colnames(allGamma))
allGamma$Band <- "Gamma"

delay_alldata <- rbind(allAlpha,allTheta) %>% rbind(., allBeta) %>% rbind(.,allGamma)
delay_alldata$epoch <- "Delay"
delay_alldata$Region <- "Whole Brain"

```
##### Gamma Band 

##### Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE}
delay_alldata_gamma <- delay_alldata %>% filter(delay_alldata$Band == "Gamma")
TP <- TrialPower(delay_alldata_gamma[])

delay_alldata_gamma %>% dplyr::filter(., Group == c(1,2)) %>% t.test(Event_Duration_Variability ~ Group, data = .)

lunaize(ggplot(data = delay_alldata_gamma[], aes(x = age, y = log1p_Trial_Power)) + geom_point() + stat_smooth(method = "lm",formula = 'y ~ x + I(x^2)') + ggtitle("Trial Power") + xlab("Age") + ylab("Trial Power (log)")) +theme(plot.title = element_text(hjust = 0.5))

```
##### Trial power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE}
TPV <- TrialPowerVar(delay_alldata_gamma)
```
##### Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE}
EN <- EventNumber(delay_alldata_gamma)

lunaize(ggplot(data = delay_alldata_gamma[], aes(x = age, y = Event_Number)) + geom_point() + stat_smooth(method = "lm",formula = 'y ~  poly(x,2)') + ggtitle("Event Number") + xlab("Age") + ylab("Event Number")) +theme(plot.title = element_text(hjust = 0.5))
```
##### Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE}
ENV <- EventNumberVar(delay_alldata_gamma)
```
##### Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE}
ED <- EventDuration(delay_alldata_gamma)
```
##### Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE}
EDV <- EventDurationVar(delay_alldata_gamma)
```

```{r, echo= FALSE, message = FALSE, warning = FALSE}

# combine all the p values so that we can correct them for multiple comparisons 
EEGPvalues <- data.frame(TP$pvalue[1], TPV$pvalue[1], EN$pvalue[1], ENV$pvalue[1], ED$pvalue[1], EDV$pvalue[1])

p.adjust((EEGPvalues), method = "bonferroni")

cowplot::plot_grid(TP$TPgraph, EN$ENgraph,ED$EDgraph,TPV$TPVgraph,ENV$ENVgraph, EDV$EDVgraph, labels = c('A','B','C','D','E','F'), label_size = 30, rel_widths = c(1,1,1.1))

cowplot::plot_grid(TP$bargraph, EN$bargraph,ED$bargraph,TPV$bargraph,ENV$bargraph, EDV$bargraph, labels = c('A','B','C','D','E','F'), label_size = 30, rel_widths = c(1,1,1.1))
```

## Fixation Period 
### Whole Brain
```{r, echo= FALSE, message = FALSE, warning = FALSE}
FixOnly <- FixOnly_Sublevel()
FixOnly_SubLevel <- FixOnly$alldata_FixOnly

alphavars <- grep("Alpha",names(FixOnly_SubLevel),value=TRUE)
allAlpha <- FixOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",alphavars)]
colnames(allAlpha) <-  sub("Alpha.", "", colnames(allAlpha))
allAlpha$Band <- "Alpha"


thetavars <- grep("Theta",names(FixOnly_SubLevel),value=TRUE)
allTheta <- FixOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",thetavars)]
colnames(allTheta) <-  sub("Theta.", "", colnames(allTheta))
allTheta$Band <- "Theta"

betavars <- grep("Beta",names(FixOnly_SubLevel),value=TRUE)
allBeta <- FixOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",betavars)]
colnames(allBeta) <-  sub("Beta.", "", colnames(allBeta))
allBeta$Band <- "Beta"


gammavars <- grep("Gamma",names(FixOnly_SubLevel),value=TRUE)
allGamma <- FixOnly_SubLevel[,c("Subject", "inverseAge", "age","Group",gammavars)]
colnames(allGamma) <-  sub("Gamma.", "", colnames(allGamma))
allGamma$Band <- "Gamma"

fix_alldata <- rbind(allAlpha,allTheta) %>% rbind(., allBeta) %>% rbind(.,allGamma)
fix_alldata$epoch <- "fix"
fix_alldata$Region <- "Whole Brain"


```
##### Gamma Band 

##### Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE}
fix_alldata_gamma <- fix_alldata %>% filter(fix_alldata$Band == "Gamma")
TP <- TrialPower(fix_alldata_gamma[])

fix_alldata_gamma %>% dplyr::filter(., Group == c(1,2)) %>% t.test(Event_Duration_Variability ~ Group, data = .)

```
##### Trial power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE}
TPV <- TrialPowerVar(fix_alldata_gamma)
```
##### Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE}
EN <- EventNumber(fix_alldata_gamma)
```
##### Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE}
ENV <- EventNumberVar(fix_alldata_gamma)
```
##### Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE}
ED <- EventDuration(fix_alldata_gamma)
```
##### Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE}
EDV <- EventDurationVar(fix_alldata_gamma)
```

```{r, echo= FALSE, message = FALSE, warning = FALSE}

# combine all the p values so that we can correct them for multiple comparisons 
EEGPvalues <- data.frame(TP$pvalue[1], TPV$pvalue[1], EN$pvalue[1], ENV$pvalue[1], ED$pvalue[1], EDV$pvalue[1])

p.adjust((EEGPvalues), method = "bonferroni")

cowplot::plot_grid(TP$TPgraph, EN$ENgraph,ED$EDgraph,TPV$TPVgraph,ENV$ENVgraph, EDV$EDVgraph, labels = c('A','B','C','D','E','F'), label_size = 30, rel_widths = c(1,1,1.1))

cowplot::plot_grid(TP$bargraph, EN$bargraph,ED$bargraph,TPV$bargraph,ENV$bargraph, EDV$bargraph, labels = c('A','B','C','D','E','F'), label_size = 30, rel_widths = c(1,1,1.1))
```

## Resting State
### Whole Brain
```{r, echo= FALSE, message = FALSE, warning = FALSE}
Restdf <- Resting_State_Data_SubjectLevel()
Restalldata <- Restdf$alldata_RestOnly

alphavars <- grep("Alpha",names(Restalldata),value=TRUE)
allAlpha <- Restalldata[,c("Subject", "inverseAge", "age","Group",alphavars)]
colnames(allAlpha) <-  sub("Alpha.", "", colnames(allAlpha))
allAlpha$Band <- "Alpha"


thetavars <- grep("Theta",names(Restalldata),value=TRUE)
allTheta <- Restalldata[,c("Subject", "inverseAge", "age","Group",thetavars)]
colnames(allTheta) <-  sub("Theta.", "", colnames(allTheta))
allTheta$Band <- "Theta"

betavars <- grep("Beta",names(Restalldata),value=TRUE)
allBeta <- Restalldata[,c("Subject", "inverseAge", "age","Group",betavars)]
colnames(allBeta) <-  sub("Beta.", "", colnames(allBeta))
allBeta$Band <- "Beta"


gammavars <- grep("Gamma",names(Restalldata),value=TRUE)
allGamma <- Restalldata[,c("Subject", "inverseAge", "age","Group",gammavars)]
colnames(allGamma) <-  sub("Gamma.", "", colnames(allGamma))
allGamma$Band <- "Gamma"

rest_alldata <- rbind(allAlpha,allTheta) %>% rbind(., allBeta) %>% rbind(.,allGamma)
rest_alldata$epoch <- "Rest"
rest_alldata$Region <- "Whole Brain"
```

##### Gamma Band 

##### Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE}
rest_alldata_gamma <- rest_alldata %>% filter(rest_alldata$Band == "Gamma")
TP <- TrialPower(rest_alldata_gamma[])

rest_alldata %>% dplyr::filter(., Group == c(2,3)) %>% t.test(Event_Duration ~ Group, data = .)


```

##### Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE}
EN <- EventNumber(rest_alldata_gamma)
```

##### Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE}
ED <- EventDuration(rest_alldata_gamma)
```


```{r, echo= FALSE, message = FALSE, warning = FALSE}

# combine all the p values so that we can correct them for multiple comparisons 
EEGPvalues <- data.frame(TP$pvalue[1], EN$pvalue[1], ED$pvalue[1])

p.adjust((EEGPvalues), method = "bonferroni")

cowplot::plot_grid(TP$TPgraph, EN$ENgraph,ED$EDgraph, labels = c('A','B','C'), label_size = 30, rel_widths = c(1,1,1.1))

cowplot::plot_grid(TP$bargraph, EN$bargraph, ED$bargraph, labels = c('A','B','C'), label_size = 30, rel_widths = c(1,1,1), ncol = 3)

```


## Delay, Fixation, and Rest
```{r, echo= FALSE, message = FALSE, warning = FALSE}
allepochs <- rbind(delay_alldata_gamma, fix_alldata_gamma )

allepochs <- rbind(allepochs, rest_alldata_gamma)
allepochs <- merge(allepochs, Behavior, by = c("Subject", "inverseAge", "age"))

  lm.model1 <- lm(data = allepochs[], Event_Duration ~ age + epoch) #if significant, regardless of epoch, theres an age effect

#TEST for a main effect of age on event duration (your main effect model)
  lm.model <- lm(data = allepochs[], Event_Duration ~ inverseAge + epoch) #if significant, regardless of epoch, theres an age effect

  AIC(lm.model,lm.model1) #check to see if age vs inverse age, which is the better model
#TEST for an interaction between age and epoch on event duration, which will tell you whether there are age effects that are most prominent in one condition vs the other
  lm.model <- lm(data = allepochs[], Event_Number ~ inverseAge*epoch) #if significant, means age effects are different across epochs 
  anova(lm.model)
lm.model <- lm(data = allepochs[allepochs$epoch=="Delay" | allepochs$epoch=="Rest",], Event_Number ~ inverseAge*epoch) #if significant, means age effects are different across epochs 
anova(lm.model)

#IF above model is significant, find out where the age effects are. ?are these called simple effects?    
  lm.model <- lm(data = allepochs[allepochs$epoch=="Delay",], Event_Duration ~ inverseAge) #only trend-level effect of age 
  lm.model <- lm(data = allepochs[allepochs$epoch=="fix",], Event_Duration ~ inverseAge) #NS effect of age
  lm.model <- lm(data = allepochs[allepochs$epoch=="Rest",], Event_Duration ~ inverseAge) #most sig age effects in rest 
  
  allepochs_wholebraingamma <- allepochs[allepochs$Band == "Gamma" & allepochs$Region == "Whole Brain",]
  
  #Bar graph of averages for spectral measures in all three epochs 
  averageEpochsbyGroup <- aggregate(. ~ Group + epoch, data = allepochs_wholebraingamma[c(4:12,14)], mean, na.rm = T)
  SDEpochsbyGroup <- aggregate(. ~ Group + epoch, data = allepochs_wholebraingamma[c(4:12,14)], sd, na.rm = T)
  
library(plotrix)
sderror<-std.error(averageEpochsbyGroup[averageEpochsbyGroup$epoch == "Delay" | averageEpochsbyGroup$epoch == "fix",]$Event_Duration_Variability)

YMIN <- averageEpochsbyGroup[averageEpochsbyGroup$epoch == "Delay" | averageEpochsbyGroup$epoch == "fix",]$Event_Duration_Variability-sderror

YMAX <- averageEpochsbyGroup[averageEpochsbyGroup$epoch == "Delay" | averageEpochsbyGroup$epoch == "fix",]$Event_Duration_Variability+sderror

lunaize(ggplot(averageEpochsbyGroup[averageEpochsbyGroup$epoch == "Delay" | averageEpochsbyGroup$epoch == "fix",], aes(x=epoch, y=log1p_Trial_Power_Variability, group = Group, fill=Group, ymin= YMIN, ymax=YMAX )) + geom_col(position = 'dodge') + geom_errorbar(position='dodge'))



#all 3 epochs
sderror<-std.error(averageEpochsbyGroup$log1p_Trial_Power)

YMIN <- averageEpochsbyGroup$log1p_Trial_Power-sderror

YMAX <- averageEpochsbyGroup$log1p_Trial_Power+sderror

lunaize(ggplot(averageEpochsbyGroup, aes(x=epoch, y=log1p_Trial_Power, group = Group, fill=Group, ymin= YMIN, ymax=YMAX )) + geom_col(position = 'dodge') + geom_errorbar(position='dodge'))

allepochs_wholebraingamma %>% dplyr::filter(., epoch == c("fix", "Delay") & Group == 1) %>% t.test(log1p_Trial_Power_Variability ~ epoch, data = .)




  #Bar graphs of averages by epoch 
  averageEpoch <-  aggregate(. ~ epoch, data = allepochs_wholebraingamma[c(4:12,14)], mean, na.rm = T)
  
sderror<-std.error(averageEpoch$Event_Duration)

YMIN <- averageEpoch$Event_Duration-sderror

YMAX <- averageEpoch$Event_Duration+sderror

lunaize(ggplot(averageEpoch, aes(x=epoch, y=Event_Duration, group = Group, fill=Group, ymin= YMIN, ymax=YMAX )) + geom_col(position = 'dodge') + geom_errorbar(position='dodge'))

allepochs_wholebraingamma %>% dplyr::filter(., epoch == c("Rest", "fix")) %>% t.test(Event_Number ~ epoch, data = .)


```

#### Gamma 
##### Whole Brain
```{r, echo= FALSE, message = FALSE, warning = FALSE}
TP <- (lunaize(ggplot(data = allepochs[], aes(x = age, y = log1p_Trial_Power, group = epoch, color = epoch)) + stat_smooth(method = "lm",formula='y~I(1/x)') + ggtitle("") + xlab("") + ylab("") + theme(legend.position = "none")))
TPV <- (lunaize(ggplot(data = allepochs[], aes(x = age, y = log1p_Trial_Power_Variability, group = epoch, color = epoch)) + stat_smooth(method = "lm",formula='y~I(1/x)') + ggtitle("") + xlab("") + ylab("")+ theme(legend.title = element_blank())))
EN <- (lunaize(ggplot(data = allepochs[], aes(x = age, y = Event_Number, group = epoch, color = epoch)) + stat_smooth(method = "lm",formula='y~I(1/x)') + ggtitle("") + xlab("") + ylab("")+ theme(legend.title = element_blank())))
ENV <- (lunaize(ggplot(data = allepochs[], aes(x = age, y = Event_Number_Variability, group = epoch, color = epoch)) + stat_smooth(method = "lm",formula='y~I(1/x)') + ggtitle("") + xlab("") + ylab("")+ theme(legend.title = element_blank())))
ED <- (lunaize(ggplot(data = allepochs[], aes(x = age, y = Event_Duration, group = epoch, color = epoch)) + stat_smooth(method = "lm",formula='y~I(1/x)') + ggtitle("") + xlab("") + ylab("")+ theme(legend.title = element_blank())))
EDV <- (lunaize(ggplot(data = allepochs[], aes(x = age, y = Event_Duration_Variability, group = epoch, color = epoch)) + stat_smooth(method = "lm",formula='y~I(1/x)')+ ggtitle("") + xlab("") + ylab("")+ theme(legend.title = element_blank()) ))


cowplot::plot_grid(TP,EN,ED,TPV,ENV,EDV, labels = c('A','B','C','D','E','F'), label_size = 30, rel_widths = c(1,1,1.1))

```

# Frequency Vs Behavior
## Best Saccade
### Delay Period
#### Whole Brain
```{r, echo= FALSE, message = FALSE, warning = FALSE}
sys.source("/Volumes/Hera/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/04.BehaviorVsEEG.R", envir = knitr::knit_global(), chdir = TRUE)

delayBehavior <- merge(Behavior, delay_alldata_gamma, by = c('Subject', 'age'))

TP <- (lunaize(ggplot(data = delayBehavior[], aes(x = absBestError, y = log1p_Trial_Power)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = delayBehavior[], log1p_Trial_Power ~ absBestError)
summary(lm.model)
 
  anova <- anova(lm.model)
  TPpvalue <- anova$`Pr(>F)`[1]
  
TPV <- (lunaize(ggplot(data = delayBehavior[], aes(x = absBestError, y = log1p_Trial_Power_Variability)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = delayBehavior[], log1p_Trial_Power_Variability ~ absBestError)
 
  anova <- anova(lm.model)
  TPVpvalue <- anova$`Pr(>F)`[1]
  
EN <- (lunaize(ggplot(data = delayBehavior[], aes(x = absBestError, y = Event_Number)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = delayBehavior[], Event_Number ~ absBestError)
 
  anova <- anova(lm.model)
  ENpvalue <- anova$`Pr(>F)`[1]
  
ENV <- (lunaize(ggplot(data = delayBehavior[], aes(x = absBestError, y = Event_Number_Variability)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = delayBehavior[], Event_Number_Variability ~ absBestError)
 
  anova <- anova(lm.model)
  ENVpvalue <- anova$`Pr(>F)`[1]
  
ED <- (lunaize(ggplot(data = delayBehavior[], aes(x = absBestError, y = Event_Duration)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = delayBehavior[], Event_Duration ~ absBestError)
 
  anova <- anova(lm.model)
  EDpvalue <- anova$`Pr(>F)`[1]


EDV <- (lunaize(ggplot(data = delayBehavior[], aes(x = absBestError, y = Event_Duration_Variability)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = delayBehavior[], Event_Duration_Variability ~ absBestError)
 
  anova <- anova(lm.model)
  EDVpvalue <- anova$`Pr(>F)`[1]
  
cowplot::plot_grid(TP,EN,ED,TPV,ENV,EDV, labels = c('A','B','C','D','E','F'), label_size = 30, rel_widths = c(1,1,1.1))

EEGPvalues <- data.frame(TPpvalue, TPVpvalue, ENpvalue, ENVpvalue, EDpvalue, EDVpvalue)

p.adjust((EEGPvalues), method = "bonferroni")

# plot by age group
lunaize(ggplot(data = delayBehavior[], aes(x = Event_Duration_Variability, y = absBestError, group = as.factor(Group), color = as.factor(Group))) + geom_point() + stat_smooth(method = "lm", alpha = 0.06) + ggtitle("") + xlab("Event Duration Var") + ylab("Best Saccade") )

lm(absBestError ~ Event_Duration_Variability, data = delayBehavior %>% filter(Group == 1)) %>% anova(.)

```

### Fixation Period
#### Whole Brain
```{r, echo= FALSE, message = FALSE, warning = FALSE}
sys.source("/Volumes/Hera/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/04.BehaviorVsEEG.R", envir = knitr::knit_global(), chdir = TRUE)

fixBehavior <- merge(Behavior, fix_alldata_gamma, by = c('Subject', 'age'))

TP <- (lunaize(ggplot(data = fixBehavior[], aes(x = absBestError, y = log1p_Trial_Power)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = fixBehavior[], log1p_Trial_Power ~ absBestError)
 
  anova <- anova(lm.model)
  TPpvalue <- anova$`Pr(>F)`[1]
  
TPV <- (lunaize(ggplot(data = fixBehavior[], aes(x = absBestError, y = log1p_Trial_Power_Variability)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = fixBehavior[], log1p_Trial_Power_Variability ~ absBestError)
 
  anova <- anova(lm.model)
  TPVpvalue <- anova$`Pr(>F)`[1]
  
EN <- (lunaize(ggplot(data = fixBehavior[], aes(x = absBestError, y = Event_Number)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = fixBehavior[], Event_Number ~ absBestError)
 
  anova <- anova(lm.model)
  ENpvalue <- anova$`Pr(>F)`[1]
  
ENV <- (lunaize(ggplot(data = fixBehavior[], aes(x = absBestError, y = Event_Number_Variability)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = fixBehavior[], Event_Number_Variability ~ absBestError)
 
  anova <- anova(lm.model)
  ENVpvalue <- anova$`Pr(>F)`[1]
  
ED <- (lunaize(ggplot(data = fixBehavior[], aes(x = absBestError, y = Event_Duration)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = fixBehavior[], Event_Duration ~ absBestError)
 
  anova <- anova(lm.model)
  EDpvalue <- anova$`Pr(>F)`[1]


EDV <- (lunaize(ggplot(data = fixBehavior[], aes(x = absBestError, y = Event_Duration_Variability)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = fixBehavior[], Event_Duration_Variability ~ absBestError)
 
  anova <- anova(lm.model)
  EDVpvalue <- anova$`Pr(>F)`[1]
  
cowplot::plot_grid(TP,EN,ED,TPV,ENV,EDV, labels = c('A','B','C','D','E','F'), label_size = 30, rel_widths = c(1,1,1.1))

EEGPvalues <- data.frame(TPpvalue, TPVpvalue, ENpvalue, ENVpvalue, EDpvalue, EDVpvalue)

p.adjust((EEGPvalues), method = "bonferroni")

# plot by age group
lunaize(ggplot(data = fixBehavior[], aes(x = Event_Duration, y = absBestError, group = as.factor(Group), color = as.factor(Group))) + geom_point() + stat_smooth(method = "lm", alpha = 0.06) + ggtitle("") + xlab("Event Duration") + ylab("Best Saccade") )

lm(absBestError ~ Event_Duration, data = fixBehavior %>% filter(Group == 1)) %>% anova(.)


```

### Resting State
#### Whole Brain
```{r, echo= FALSE, message = FALSE, warning = FALSE}
sys.source("/Volumes/Hera/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/04.BehaviorVsEEG.R", envir = knitr::knit_global(), chdir = TRUE)

restBehavior <- merge(Behavior, rest_alldata_gamma, by = c('Subject', 'age'))

TP <- (lunaize(ggplot(data = restBehavior[], aes(x = absBestError, y = log1p_Trial_Power)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = restBehavior[], log1p_Trial_Power ~ absBestError)
 
  anova <- anova(lm.model)
  TPpvalue <- anova$`Pr(>F)`[1]
  
TPV <- (lunaize(ggplot(data = restBehavior[], aes(x = absBestError, y = log1p_Trial_Power_Variability)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = restBehavior[], log1p_Trial_Power_Variability ~ absBestError)
 
  anova <- anova(lm.model)
  TPVpvalue <- anova$`Pr(>F)`[1]
  
EN <- (lunaize(ggplot(data = restBehavior[], aes(x = absBestError, y = Event_Number)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = restBehavior[], Event_Number ~ absBestError)
 
  anova <- anova(lm.model)
  ENpvalue <- anova$`Pr(>F)`[1]
  
ENV <- (lunaize(ggplot(data = restBehavior[], aes(x = absBestError, y = Event_Number_Variability)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = restBehavior[], Event_Number_Variability ~ absBestError)
 
  anova <- anova(lm.model)
  ENVpvalue <- anova$`Pr(>F)`[1]
  
ED <- (lunaize(ggplot(data = restBehavior[], aes(x = absBestError, y = Event_Duration)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = restBehavior[], Event_Duration ~ absBestError)
 
  anova <- anova(lm.model)
  EDpvalue <- anova$`Pr(>F)`[1]


EDV <- (lunaize(ggplot(data = restBehavior[], aes(x = absBestError, y = Event_Duration_Variability)) + geom_point() + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") ))
lm.model <- lm(data = restBehavior[], Event_Duration_Variability ~ absBestError)
 
  anova <- anova(lm.model)
  EDVpvalue <- anova$`Pr(>F)`[1]
  
cowplot::plot_grid(TP,EN,ED,TPV,ENV,EDV, labels = c('A','B','C','D','E','F'), label_size = 30, rel_widths = c(1,1,1.1))

EEGPvalues <- data.frame(TPpvalue, TPVpvalue, ENpvalue, ENVpvalue, EDpvalue, EDVpvalue)

p.adjust((EEGPvalues), method = "bonferroni")

#age groups
lunaize(ggplot(data = restBehavior[], aes(x = Event_Number, y = absBestError, group = as.factor(Group), color = as.factor(Group))) + geom_point() + stat_smooth(method = "lm", alpha = 0.06) + ggtitle("") + xlab("Event Number") + ylab("Best Saccade") )

lm(absBestError ~ Event_Number, data = restBehavior %>% filter(Group == 1)) %>% anova(.)


```

## Delay, Fixation, and Rest
```{r, echo= FALSE, message = FALSE, warning = FALSE}
allepochs <- rbind(delay_alldata_gamma, fix_alldata_gamma )

allepochs <- rbind(allepochs, rest_alldata_gamma)
allepochs <- merge(allepochs, Behavior, by = c("Subject", "age"))
```
### Gamma
#### Whole Brain
```{r, echo= FALSE, message = FALSE, warning = FALSE}
TP <- lunaize(ggplot(data = allepochs[], aes(x = absBestError, y = log1p_Trial_Power, group = epoch, color = epoch))  + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") )

TPV <- lunaize(ggplot(data = allepochs[], aes(x = absBestError, y = log1p_Trial_Power_Variability, group = epoch, color = epoch))  + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") )

EN <- lunaize(ggplot(data = allepochs[], aes(x = absBestError, y = Event_Number, group = epoch, color = epoch))  + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") )

ENV <- lunaize(ggplot(data = allepochs[], aes(x = absBestError, y = Event_Number_Variability, group = epoch, color = epoch))  + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") )

ED <- lunaize(ggplot(data = allepochs[], aes(x = absBestError, y = Event_Duration, group = epoch, color = epoch))  + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") )

EDV <- lunaize(ggplot(data = allepochs[], aes(x = absBestError, y = Event_Duration_Variability, group = epoch, color = epoch))  + stat_smooth(method = "lm") + ggtitle("") + xlab("") + ylab("") )


cowplot::plot_grid(TP,EN,ED,TPV,ENV,EDV, labels = c('A','B','C','D','E','F'), label_size = 30, rel_widths = c(1,1,1.1))


```