---
title: "Spectral Events Frequency vs Age"
author: "Shane McKeon"
date: "11/16/2020"
geometry: margin = 1in
output:
  pdf_document:  
    toc: true
    toc_depth: 4    
    fig_caption: yes
  latex_engine: xelatex

  html_document:
    df_print: paged
    code_folding: hide 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev='png', dpi=150, fig.width = 6, fig.height=6, fig.align = 'left', fig.margin = TRUE)
```


```{r load-libraries, message=FALSE}
```


```{r, echo= FALSE, message = FALSE, warning = FALSE}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, ggplot2,lme4, multcomp, tidyr, tidyverse,wesanderson, reshape2, corrplot, ggExtra, cowplot, ggsci, mgcv, ggpointdensity, devtools, ggpubr, itsadug, useful, rmarkdown, tinytex, gratia, gamm4, car, GGally, CCA)

#devtools::install_github('LabneuroCogDevel/LNCDR')
#library(devtools)
#devtools::install_github("strengejacke/sjPlot")
library(LNCDR)
library(data.table)
require(dplyr)
library(factoextra)
library(tidyverse)
require(knitr)
library(ggplot2)
library(e1071)
library(caret)
library(sjPlot)
library(directlabels)

```

# Frequency Bands Across Age 
```{r  echo=FALSE, message=FALSE, warning=FALSE, cashe = FALSE, include = TRUE}

sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)


#only delay variables, trial level
# alldf_trialLevel <- Only_Take_One_Delay_Bin_TrialLevel()
# alldata_TrialLevel <- alldf_trialLevel$alldata_TrialLevel
# alldata_TrialLevel$Task <- "Delay"


#only the delay variables at the subject level 
alldf_subLevel <- DelayOnly_Sublevel()
delayOnly_SubLevel <- alldf_subLevel$alldata_delayOnly


# #resting state at the trial level 
# alldf_RS <- Resting_State_Data_TrialLevel()
# alldata_RS <- alldf_RS$alldata_TrialLevel
# alldata_RS$Task <- "Rest"

#resting state at the subject level
alldf_SubjectLevel_RS <- Resting_State_Data_SubjectLevel()
alldata_RS_SubLevel <- alldf_SubjectLevel_RS$alldata_TrialLevel
alldata_RS_SubLevel$Task <- "Rest"
alldata_RS_SubLevel <- subset(alldata_RS_SubLevel, select = -Trial)

#merging delay and rest, at the subject level 
delayRest <- merge(alldata, alldata_RS_SubLevel[1:30], by = "Subject")
delayRest_long <- rbind(delayOnly, alldata_RS_SubLevel)

#merging delay and rest, at the trial level
delayRest_long_trialLevel <- rbind(alldata_RS, alldata_trialLevel)

```

## Delay Period
### Average Trial Power
```{r  echo=FALSE, message=FALSE, warning=FALSE, cashe = FALSE, include = TRUE}
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/02.FrequencyAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)

AverageTrialPower(delayOnly_SubLevel)
```

### Trial Power Variability 
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
# this has to be done at the sub level 
TrialPowerVariability(delayOnly_SubLevel)
```

### Number of Events
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
NumberofEvents(alldata_TrialLevel)
```

#### Gamma:Beta Ratio
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
alldata_trialLevel$RatioNumberofEvents <- alldata_trialLevel$Gamma.Event_Number/alldata_trialLevel$Beta.Event_Number
alldata_trialLevel$RatioNumberofEvents[which(is.infinite(alldata_trialLevel$RatioNumberofEvents))] <- 0

cleandata <-  alldata_trialLevel %>% filter(abs(RatioNumberofEvents - mean(RatioNumberofEvents, na.rm= T)) < (sd(RatioNumberofEvents, na.rm= T) * 2))

lunaize(ggplot(data = cleandata, aes(x = age, y = RatioNumberofEvents)) + stat_smooth(method = 'lm',  formula='y~I(1/x)')+ ylab('Gamma:Beta Number of Events') + xlab('Age') + ggtitle('Gamma:Beta \nNumber of Events vs Age'))  + theme(plot.title = element_text(hjust = 0.5))

 lm.model <- lmer(data = cleandata, RatioNumberofEvents ~ inverseAge + (1|Subject))
 print(car::Anova(lm.model))
  


```

#### Gamma:Beta Ratio Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
alldata_trialLevel$RatioNumberofEvents <- alldata_trialLevel$Gamma.Event_Number/alldata_trialLevel$Beta.Event_Number
alldata_trialLevel$RatioNumberofEvents[which(is.infinite(alldata_trialLevel$RatioNumberofEvents))] <- 0

cleandata <-  alldata_trialLevel %>% filter(abs(RatioNumberofEvents - mean(RatioNumberofEvents, na.rm= T)) < (sd(RatioNumberofEvents, na.rm= T) * 2))

sd_cleanData <- aggregate(. ~ Subject, cleandata, sd)
sd_cleanData <- merge(sd_cleanData, agefile, by = 'Subject')
sd_cleanData$inverseAge <- 1/sd_cleanData$age.y

lunaize(ggplot(data = sd_cleanData, aes(x = age.y, y = RatioNumberofEvents)) + stat_smooth(method = 'lm',  formula='y~I(1/x)')+ ylab('Gamma:Beta Number of Events Variability') + xlab('Age') + ggtitle('Gamma:Beta Variability \nNumber of Events vs Age'))  + theme(plot.title = element_text(hjust = 0.5))

 lm.model <- lm(data = sd_cleanData, RatioNumberofEvents ~ inverseAge)
 print(car::Anova(lm.model))
  


```

### Number of Events Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
NumberofEventsVariability(delayOnly_SubLevel)
```

### Duration of Events
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DurationofEvents(alldata_TrialLevel)
```

### Duration of Events Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DurationofEventsVariability(delayOnly_SubLevel)
```

## Fixation Period
### Average Trial Power
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/02.FrequencyAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)

AverageTrialPowerFix()
```

### Trial Power Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
TrialPowerVariabilityFix()
```


### Number of Events
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
NumberofEventsFix()
```

### Number of Events Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
NumberofEventsVariabilityFix()
```

### Duration of Events
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DurationofEventsFix()
```

### Duration of Events Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DurationofEventsVariabilityFix()
```

## Delay Minus Fix
### Delay Minus Fix Trial Power
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusFix()
DelayMinusFix_TrialPower()
```

### Delay Minus Fix Trial Power Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusFix_TrialPowerVar()
```

### Delay Minus Fix Event Number
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusFix_EventNumber()
```

### Delay Minus Fix Event Number Variability 
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusFix_EventNumberVar()
```

### Delay Minus Fix Event Duration
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusFix_EventDuration()
```

### Delay Minus Fix Event Duration Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusFix_EventDurationVar()
```




## Resting State 
### Average Trial Power
```{r  echo=FALSE, message=FALSE, warning=FALSE, cashe = FALSE, include = TRUE}
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/02.FrequencyAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)

AverageTrialPowerRS()

#Doing outlier detection 
delayRest_long_TrialLevel_outlierDetection  <- delayRest_long_trialLevel %>% group_by(Subject) %>% filter(abs(Gamma.log1p_Trial_Power - mean(Gamma.log1p_Trial_Power, na.rm= T)) < (sd(Gamma.log1p_Trial_Power, na.rm = T) * 2)) 
  

#plotting delay and rest age vs gamma power in one plot
lunaize(ggplot(data = delayRest_long_TrialLevel_outlierDetection[delayRest_long_TrialLevel_outlierDetection$visitno <2,], aes(x = age, y = Gamma.log1p_Trial_Power, group = Task, color = Task)) + stat_smooth(method = 'lm',  formula='y~I(1/x)') + xlab("Age") + ylab("log(Trial Power)"))

 
  lm.model <- lm(data = delayRest_long_TrialLevel_outlierDetection[delayRest_long_TrialLevel_outlierDetection$visitno < 2 & delayRest_long_TrialLevel_outlierDetection$Task == 'Delay',], Gamma.log1p_Trial_Power ~ inverseAge)
  print(anova(lm.model))
```

### Trial Power Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
TrialPowerVariabilityRS()
```

### Number of Events
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
NumberofEventsRS()

#OUTLIER DETECTION
delayRest_long_TrialLevel_outlierDetection  <- delayRest_long_trialLevel %>% group_by(Subject) %>% filter(abs(Gamma.Event_Number - mean(Gamma.Event_Number, na.rm= T)) < (sd(Gamma.Event_Number, na.rm = T) * 2)) 

#interaction on sub level
EventAgeInteraction <- lm(Gamma.Event_Number ~ age * Task, data = delayRest_long)
car::Anova(EventAgeInteraction)
summary(EventAgeInteraction)

#interaction on trial level
EventAgeInteraction_trialLevel <- lmer(Gamma.Event_Number ~ age*Task + (1|Subject), data = delayRest_long_trialLevel)
car::Anova(EventAgeInteraction_trialLevel)
summary(EventAgeInteraction_trialLevel)

#plotting delay and rest age vs gamma event numbers in one plot
lunaize(ggplot(data = delayRest_long_TrialLevel_outlierDetection[delayRest_long_TrialLevel_outlierDetection$visitno <2,], aes(x = age, y = Gamma.Event_Number, group = Task, color = Task)) + stat_smooth(method = 'lm',  formula='y~I(1/x)') + xlab("Age") + ylab("Number of Events"))

  
  lm.model <- lm(data = delayRest_long_TrialLevel_outlierDetection[delayRest_long_TrialLevel_outlierDetection$visitno < 2 & delayRest_long_TrialLevel_outlierDetection$Task == 'Rest',], Gamma.Event_Number ~ inverseAge)
  print(anova(lm.model))

```

### Number of Events Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
NumberofEventsVariabilityRS()
```

### Duration of Events
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DurationofEventsRS()

#plotting delay and rest age vs gamma event duration in one plot
lunaize(ggplot(data = delayRest_long_trialLevel, aes(x = age, y = Gamma.Event_Duration, group = Task, color = Task)) + stat_smooth(method = 'lm',  formula='y~I(1/x)') + xlab("Age") + ylab("Duration of Events"))
```

### Duration of Events Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DurationofEventsVariabilityRS()
```

#Delay Minus Resting State
## Delay Minus Rest Trial Power
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusRest()
DelayMinusRest_TrialPower()
```

## Delay Minus Rest Trial Power Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusRest_TrialPowerVar()
```

## Delay Minus Rest Event Number
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusRest_EventNumber()
```

## Delay Minus Rest Event Number Variability 
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusRest_EventNumberVar()
```

## Delay Minus Rest Event Duration
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusRest_EventDuration()
```

## Delay Minus Rest Event Duration Variability
```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}
DelayMinusRest_EventDurationVar()
```


# Rest-Delay/Delay Percent Change 
## Trial Power

```{r  echo=FALSE, message=FALSE, warning=FALSE, include = TRUE}

sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)

alldf_Rs <- Resting_State_Data_SubjectLevel()
rest_SubLevel <- alldf_Rs$rest_SubLevel

alldf <- DelayOnly_Sublevel()
delay_SubLevel <- alldf$alldata_delayOnly

restDelay_SubLevel <- merge(delay_SubLevel, rest_SubLevel, by = "Subject", suffixes = c("_Delay", "_Rest"))

restDelay_SubLevel$PercentChange <- (restDelay_SubLevel$Gamma.log1p_Trial_Power_Rest - restDelay_SubLevel$Gamma.log1p_Trial_Power_Delay) / restDelay_SubLevel$Gamma.log1p_Trial_Power_Delay

lunaize(ggplot(data = restDelay_SubLevel, aes(x = age_Delay, y = PercentChange)) + stat_smooth(method = 'lm', formula = 'y~I(1/x)') + xlab("Age") + ylab("Percent Change"))

lm.model <- lm(data = restDelay_SubLevel, PercentChange ~ inverseAge_Delay)
anova(lm.model)

```








