---
title: "Spectral Events EEG vs Behavior"
author: "Shane McKeon"
date: "11/16/2020"
geometry: margin = 1in
output:
  pdf_document:  
    toc: true
    toc_depth: 4    
    fig_caption: yes
  latex_engine: xelatex

  html_document:
    df_print: paged
    code_folding: hide 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev='png', dpi=150, fig.width = 6, fig.height=6, fig.align = 'left', fig.margin = TRUE)
```


```{r load-libraries, message=FALSE}
```


```{r, echo= FALSE, message = FALSE, warning = FALSE}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, ggplot2,lme4, multcomp, tidyr, tidyverse,wesanderson, reshape2, corrplot, ggExtra, cowplot, ggsci, mgcv, ggpointdensity, devtools, ggpubr, itsadug, useful, rmarkdown, tinytex, gratia, gamm4, car, GGally, CCA)

#devtools::install_github('LabneuroCogDevel/LNCDR')
#library(devtools)
#devtools::install_github("strengejacke/sjPlot")
library(LNCDR)
library(data.table)
require(dplyr)
library(factoextra)
library(tidyverse)
require(knitr)
library(ggplot2)
library(e1071)
library(caret)

```


```{r  echo=FALSE, message=FALSE, warning=FALSE, cashe = FALSE, include = TRUE}

sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R", envir = knitr::knit_global(), chdir = TRUE)
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/02.FrequencyAcrossAge.R", envir = knitr::knit_global(), chdir = TRUE)
sys.source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/09.EEGvsBehavior.R", envir = knitr::knit_global(), chdir = TRUE)


alldf <- Only_Take_One_Delay_Bin_and_Fix()
alldata <- alldf$alldata

# on the subject level
alldata_DelayminusFix <- DelayMinusFix()

# delay only on the trial level 
alldf <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf$alldata_TrialLevel

Behavior <- read.csv('H:/Projects/7TBrainMech/scripts/eeg/Shane/Results/Power_Analysis/Spectral_events_analysis/Behavior_20200921.csv')
agefile <- read.csv('H:/Projects/7TBrainMech/scripts/eeg/Shane/Results/Power_Analysis/Spectral_events_analysis/agefile_20210204.csv')

#behavioral data contains each trial 
Behavior$Subject <- paste0(Behavior$LunaID, '_', Behavior$ScanDate)
Behavior$absPositionError <- abs(Behavior$PositionError)

alldata_TrialLevel_Behavior <- merge(alldata_TrialLevel, Behavior, by = c("Subject", "Trial"))
alldata_TrialLevel_Behavior$Group <- factor(alldata_TrialLevel_Behavior$Group)




```

# EEG Activity vs. Behavior Subject Level
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/09.EEGvsBehavior.R")
```

## Delay Period
### Position Error
#### Gamma Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.log1p_Trial_Power_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Number_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Duration_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.log1p_Trial_Power_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Number_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Duration_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```


#### Beta Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.log1p_Trial_Power_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Number_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Duration_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.log1p_Trial_Power_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Number_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Duration_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

#### Alpha Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.log1p_Trial_Power_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Number_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Duration_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.log1p_Trial_Power_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Number_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Duration_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

#### Theta Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.log1p_Trial_Power_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Number_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Duration_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.log1p_Trial_Power_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Number_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Duration_Variability_Delay", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

#### Gamma:Beta Ratio
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}
 
alldata_TrialLevel_Behavior$RatioNumberofEvents <- alldata_TrialLevel_Behavior$Gamma.Event_Number/alldata_TrialLevel_Behavior$Beta.Event_Number
alldata_TrialLevel_Behavior$RatioNumberofEvents[which(is.infinite(alldata_TrialLevel_Behavior$RatioNumberofEvents))] <- 0

cleandata <-  alldata_TrialLevel_Behavior %>% filter(abs(RatioNumberofEvents - mean(RatioNumberofEvents, na.rm= T)) < (sd(RatioNumberofEvents, na.rm= T) * 2)) %>% filter(abs(PositionError - mean(PositionError, na.rm= T)) < (sd(PositionError, na.rm= T) * 2))

# all together 
lunaize(ggplot(data = cleandata, aes(x = absPositionError, y = RatioNumberofEvents)) + stat_smooth(method = 'lm')+ ylab('Gamma:Beta Number of Events') + xlab('abs(Position Error)') + ggtitle('Gamma:Beta \nNumber of Events vs Accuracy'))  + theme(plot.title = element_text(hjust = 0.5))

 lm.model <- lmer(data = cleandata, RatioNumberofEvents ~ absPositionError + (1|Subject))
 print(car::Anova(lm.model))
 
 # split by age group 
lunaize(ggplot(data = cleandata, aes(x = RatioNumberofEvents, y = absPositionError, group = Group, color = Group)) + stat_smooth(method = 'lm', se = F)+ ylab('abs(Position Error)') + xlab('Gamma:Beta Number of Events') + ggtitle('Gamma:Beta \nNumber of Events vs Position Error'))  + theme(plot.title = element_text(hjust = 0.5))

 lm.model <- lmer(data = cleandata[cleandata$Group == 4,], absPositionError ~ RatioNumberofEvents+ (1|Subject))
 print(car::Anova(lm.model))
 
```

#### Gamma:Beta Ratio Variability 
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

alldata_TrialLevel_Behavior$RatioNumberofEvents <- alldata_TrialLevel_Behavior$Gamma.Event_Number/alldata_TrialLevel_Behavior$Beta.Event_Number
alldata_TrialLevel_Behavior$RatioNumberofEvents[which(is.infinite(alldata_TrialLevel_Behavior$RatioNumberofEvents))] <- 0

cleandata <-  alldata_TrialLevel_Behavior %>% filter(abs(RatioNumberofEvents - mean(RatioNumberofEvents, na.rm= T)) < (sd(RatioNumberofEvents, na.rm= T) * 2)) %>% filter(abs(PositionError - mean(PositionError, na.rm= T)) < (sd(PositionError, na.rm= T) * 2))

avg_cleanData <- aggregate(. ~ Subject, cleandata, mean)
sd_cleanData <- aggregate(. ~ Subject, cleandata, sd)
sd_cleanData <- merge(sd_cleanData, agefile, by = 'Subject')
sd_cleanData$Group.y <- factor(sd_cleanData$Group.y)

#all together
lunaize(ggplot(data = sd_cleanData, aes(x = absPositionError, y = RatioNumberofEvents)) + stat_smooth(method = 'lm')+ ylab('Gamma:Beta Number of Events Variability') + xlab('Accuracy Variability') + ggtitle('Gamma:Beta Variability \nNumber of Events vs Accuracy'))  + theme(plot.title = element_text(hjust = 0.5))

lm.model <- lm(data = sd_cleanData, RatioNumberofEvents ~ absPositionError)
 print(car::Anova(lm.model))
 
  # split by age group 
lunaize(ggplot(data = sd_cleanData, aes(x = RatioNumberofEvents, y = absPositionError, group = Group.y, color = Group.y)) + stat_smooth(method = 'lm', se = F)+ ylab('Accuracy Variability') + xlab('Gamma:Beta Number of Events Variability') + ggtitle('Gamma:Beta Variability \nNumber of Events vs Accuracy'))  + theme(plot.title = element_text(hjust = 0.5))

 lm.model <- lm(data = sd_cleanData[sd_cleanData$Group.y == 1,], absPositionError ~ RatioNumberofEvents)
 print(car::Anova(lm.model))

```


### MGS Latency
#### Gamma Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.log1p_Trial_Power_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Number_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Duration_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.log1p_Trial_Power_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Number_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Duration_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```


#### Beta Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.log1p_Trial_Power_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Number_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Duration_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.log1p_Trial_Power_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Number_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Duration_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

#### Alpha Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.log1p_Trial_Power_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Number_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Duration_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.log1p_Trial_Power_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Number_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Duration_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

#### Theta Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.log1p_Trial_Power_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Number_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Duration_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.log1p_Trial_Power_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Number_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Duration_Variability_Delay", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```
#### Gamma:Beta Ratio
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}
 
alldata_TrialLevel_Behavior$RatioNumberofEvents <- alldata_TrialLevel_Behavior$Gamma.Event_Number/alldata_TrialLevel_Behavior$Beta.Event_Number
alldata_TrialLevel_Behavior$RatioNumberofEvents[which(is.infinite(alldata_TrialLevel_Behavior$RatioNumberofEvents))] <- 0

cleandata <-  alldata_TrialLevel_Behavior %>% filter(abs(RatioNumberofEvents - mean(RatioNumberofEvents, na.rm= T)) < (sd(RatioNumberofEvents, na.rm= T) * 2)) %>% filter(abs(mgsLatency - mean(mgsLatency, na.rm= T)) < (sd(mgsLatency, na.rm= T) * 2))

# all together 
lunaize(ggplot(data = cleandata, aes(x = mgsLatency, y = RatioNumberofEvents)) + stat_smooth(method = 'lm')+ ylab('Gamma:Beta Number of Events') + xlab('mgs Latency') + ggtitle('Gamma:Beta \nNumber of Events vs Latency'))  + theme(plot.title = element_text(hjust = 0.5))

 lm.model <- lmer(data = cleandata, RatioNumberofEvents ~ mgsLatency + (1|Subject))
 print(car::Anova(lm.model))
 
 # split by age group 
lunaize(ggplot(data = cleandata, aes(x = RatioNumberofEvents, y = mgsLatency, group = Group, color = Group)) + stat_smooth(method = 'lm', se = F)+ ylab('mgs Latency') + xlab('Gamma:Beta Number of Events') + ggtitle('Gamma:Beta \nNumber of Events vs Latency'))  + theme(plot.title = element_text(hjust = 0.5))

 lm.model <- lmer(data = cleandata[cleandata$Group == 1,], mgsLatency ~ RatioNumberofEvents+ (1|Subject))
 print(car::Anova(lm.model))
 
```

#### Gamma:Beta Ratio Variability 
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

alldata_TrialLevel_Behavior$RatioNumberofEvents <- alldata_TrialLevel_Behavior$Gamma.Event_Number/alldata_TrialLevel_Behavior$Beta.Event_Number
alldata_TrialLevel_Behavior$RatioNumberofEvents[which(is.infinite(alldata_TrialLevel_Behavior$RatioNumberofEvents))] <- 0

cleandata <-  alldata_TrialLevel_Behavior %>% filter(abs(RatioNumberofEvents - mean(RatioNumberofEvents, na.rm= T)) < (sd(RatioNumberofEvents, na.rm= T) * 2)) %>% filter(abs(mgsLatency - mean(mgsLatency, na.rm= T)) < (sd(mgsLatency, na.rm= T) * 2))

avg_cleanData <- aggregate(. ~ Subject, cleandata, mean)
sd_cleanData <- aggregate(. ~ Subject, cleandata, sd)
sd_cleanData <- merge(sd_cleanData, agefile, by = 'Subject')
sd_cleanData$Group.y <- factor(sd_cleanData$Group.y)

#all together
lunaize(ggplot(data = sd_cleanData, aes(x = mgsLatency, y = RatioNumberofEvents)) + stat_smooth(method = 'lm')+ ylab('Gamma:Beta Number of Events Variability') + xlab('mgs Latency Variability') + ggtitle('Gamma:Beta Variability \nNumber of Events vs Latency'))  + theme(plot.title = element_text(hjust = 0.5))

lm.model <- lm(data = sd_cleanData, RatioNumberofEvents ~ mgsLatency)
 print(car::Anova(lm.model))
 
  # split by age group 
lunaize(ggplot(data = sd_cleanData, aes(x = RatioNumberofEvents, y = mgsLatency, group = Group.y, color = Group.y)) + stat_smooth(method = 'lm', se = F)+ ylab('mgs Latency Variability') + xlab('Gamma:Beta Number of Events Variability') + ggtitle('Gamma:Beta Variability \nNumber of Events vs Latency'))  + theme(plot.title = element_text(hjust = 0.5))

 lm.model <- lm(data = sd_cleanData[sd_cleanData$Group.y == 4,], mgsLatency ~ RatioNumberofEvents)
 print(car::Anova(lm.model))

```



## Fixation Period
### Position Error
#### Gamma Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.log1p_Trial_Power_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Number_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Duration_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.log1p_Trial_Power_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Number_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Duration_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```


#### Beta Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.log1p_Trial_Power_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Number_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Duration_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.log1p_Trial_Power_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Number_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Duration_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

#### Alpha Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.log1p_Trial_Power_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Number_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Duration_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.log1p_Trial_Power_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Number_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Duration_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

#### Theta Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.log1p_Trial_Power_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Number_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Duration_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.log1p_Trial_Power_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Number_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Duration_Variability_Fix", "absPositionError") 
EEGvsBehavior(selected_vars, alldata)

```


### MGS Latency
#### Gamma Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.log1p_Trial_Power_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Number_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Duration_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.log1p_Trial_Power_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Number_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Gamma.Event_Duration_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```


#### Beta Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.log1p_Trial_Power_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Number_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Duration_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.log1p_Trial_Power_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Number_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Beta.Event_Duration_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

#### Alpha Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.log1p_Trial_Power_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Number_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Duration_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.log1p_Trial_Power_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Number_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Alpha.Event_Duration_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

#### Theta Frequency Band
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.log1p_Trial_Power_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Number_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Duration_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.log1p_Trial_Power_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Number_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

selected_vars <-c("Theta.Event_Duration_Variability_Fix", "mgsLatency") 
EEGvsBehavior(selected_vars, alldata)

```


# Delay Minus Fixation Subject Level 
## Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

DelayMinusFixvsBehavior_TrialPower()

```


## Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

DelayMinusFixvsBehavior_TrialPowerVar()

```


## Event Number 
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

DelayMinusFixvsBehavior_EventNumber()

```

## Event Number Variability 
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

DelayMinusFixvsBehavior_EventNumberVar()

```

## Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

DelayMinusFixvsBehavior_EventDuration()

```


## Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

DelayMinusFixvsBehavior_EventDurationVar()

```



## Event Number Adults Only
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}

DelayMinusFixvsBehavior_EventNumber_AdultsOnly()

```



#EEG Avtivity vs. Behavior Trial Level
## Delay Period

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}
alldf_TrialLevel <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf_TrialLevel$alldata_TrialLevel

DelayvsBehavior_TrialLevel()

```
## Fixation Period

```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}
alldf_Fix_TrialLevel <- Only_Take_Fix_TrialLevel()
alldata_Fix_TrialLevel <- alldf_Fix_TrialLevel$alldata_Fix_TrialLevel

FixvsBehavior_TrialLevel()

```

# Delay Minus Fixation Trial Level 
## Event Number 
```{r, echo= FALSE, message = FALSE, warning = FALSE, results='hide', fig.keep='all'}
DelayMinusFixvsBehavior_TrialLevel()

```



