---
title: "Spectral Events Mediation Analyses"
author: "Shane McKeon"
date: "11/16/2020"
geometry: margin = 1in
output:
  pdf_document:  
    toc: true
    toc_depth: 4    
    fig_caption: yes
  latex_engine: xelatex

  html_document:
    df_print: paged
    code_folding: hide 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev='png', dpi=150, fig.width = 6, fig.height=6, fig.align = 'left', fig.margin = TRUE)
```


```{r load-libraries, message=FALSE}
```


```{r, echo= FALSE, message = FALSE, warning = FALSE}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, ggplot2,lme4, multcomp, tidyr, tidyverse,wesanderson, reshape2, corrplot, ggExtra, cowplot, ggsci, mgcv, ggpointdensity, devtools, ggpubr, itsadug, useful, rmarkdown, tinytex, gratia, gamm4, car, GGally, CCA)

#devtools::install_github('LabneuroCogDevel/LNCDR')
#library(devtools)
#devtools::install_github("strengejacke/sjPlot")
library(LNCDR)
library(data.table)
require(dplyr)
library(factoextra)
library(tidyverse)
require(knitr)
library(ggplot2)
library(e1071)
library(caret)

```



# Mediation Analysis: Trial Level
## Delay Period
### Position Error
#### Gamma Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
```


```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")

alldf <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf$alldata_TrialLevel

other_vars <-c("Gamma.log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel, other_vars)
```




##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf$alldata_TrialLevel

alldata_TrialLevel_youngest <- alldata_TrialLevel[alldata_TrialLevel$Group == 1,]
alldata_TrialLevel_Secondyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 2,]
alldata_TrialLevel_thirdyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 3,]
alldata_TrialLevel_oldest <- alldata_TrialLevel[alldata_TrialLevel$Group == 4,]

other_vars <-c("Gamma.log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel_oldest, other_vars)


```

#### Gamma Event Number

```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma.Event_Number", "absPositionError") #define what you want in the mediation analysis

MediationAnalysis(alldata_TrialLevel, other_vars)

```

##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf$alldata_TrialLevel

alldata_TrialLevel_youngest <- alldata_TrialLevel[alldata_TrialLevel$Group == 1,]
alldata_TrialLevel_Secondyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 2,]
alldata_TrialLevel_thirdyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 3,]
alldata_TrialLevel_oldest <- alldata_TrialLevel[alldata_TrialLevel$Group == 4,]

other_vars <-c("Gamma.Event_Number", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel_oldest, other_vars)


```

#### Gamma Event Number and power 

```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma_Event_Number", "Gamma_log1p_Trial_Power") #define what you want in the mediation analysis

MediationAnalysis(other_vars)

```

#### Gamma Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Gamma.Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel, other_vars)

```

##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf$alldata_TrialLevel

alldata_TrialLevel_youngest <- alldata_TrialLevel[alldata_TrialLevel$Group == 1,]
alldata_TrialLevel_Secondyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 2,]
alldata_TrialLevel_thirdyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 3,]
alldata_TrialLevel_oldest <- alldata_TrialLevel[alldata_TrialLevel$Group == 4,]

other_vars <-c("Gamma.Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel_thirdyoungest, other_vars)
```

#### Beta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta.log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel, other_vars)

```
#### Beta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta.Event_Number", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel,other_vars)

```

#### Beta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta.Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel, other_vars)

```

#### Alpha Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha.log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel, other_vars)

```

#### Alpha Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha.Event_Number", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis(alldata_TrialLevel, other_vars)

```

#### Alpha Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha.Event_Duration", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis(alldata_TrialLevel, other_vars)

```

#### Theta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis(other_vars)

```

#### Theta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Number", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis(other_vars)

```

#### Theta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Duration", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis(other_vars)

```

### Latency
#### Gamma Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")

alldf <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf$alldata_TrialLevel

other_vars <-c("Gamma.log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel, other_vars)

```

##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf$alldata_TrialLevel

alldata_TrialLevel_youngest <- alldata_TrialLevel[alldata_TrialLevel$Group == 1,]
alldata_TrialLevel_Secondyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 2,]
alldata_TrialLevel_thirdyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 3,]
alldata_TrialLevel_oldest <- alldata_TrialLevel[alldata_TrialLevel$Group == 4,]

other_vars <-c("Gamma.log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel_oldest, other_vars)


```

#### Gamma Event Number

```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma.Event_Number", "mgsLatency") #define what you want in the mediation analysis

MediationAnalysis(alldata_TrialLevel, other_vars)

```


##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf$alldata_TrialLevel

alldata_TrialLevel_youngest <- alldata_TrialLevel[alldata_TrialLevel$Group == 1,]
alldata_TrialLevel_Secondyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 2,]
alldata_TrialLevel_thirdyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 3,]
alldata_TrialLevel_oldest <- alldata_TrialLevel[alldata_TrialLevel$Group == 4,]

other_vars <-c("Gamma.Event_Number", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel_oldest, other_vars)


```

#### Gamma Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Gamma.Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel, other_vars)

```

##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf <- Only_Take_One_Delay_Bin_TrialLevel()
alldata_TrialLevel <- alldf$alldata_TrialLevel

alldata_TrialLevel_youngest <- alldata_TrialLevel[alldata_TrialLevel$Group == 1,]
alldata_TrialLevel_Secondyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 2,]
alldata_TrialLevel_thirdyoungest <- alldata_TrialLevel[alldata_TrialLevel$Group == 3,]
alldata_TrialLevel_oldest <- alldata_TrialLevel[alldata_TrialLevel$Group == 4,]

other_vars <-c("Gamma.Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel_thirdyoungest, other_vars)


```

#### Beta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis(other_vars)

```

#### Beta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_Event_Number", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis(other_vars)

```

#### Beta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta.Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel,other_vars)

```

#### Alpha Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha.log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis(alldata_TrialLevel,other_vars)

```

#### Alpha Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha.Event_Number", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis(alldata_TrialLevel,other_vars)

```

#### Alpha Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha.Event_Duration", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis(alldata_TrialLevel,other_vars)

```

#### Theta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis(other_vars)

```
#### Theta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Number", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis(other_vars)

```
#### Theta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Duration", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis(other_vars)

```


## Fixation Period
### Position Error
#### Gamma Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma_log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```
#### Gamma Event Number

```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma_Event_Number", "absPositionError") #define what you want in the mediation analysis

MediationAnalysisFixation(other_vars)

```

#### Gamma Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Gamma_Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Beta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Beta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_Event_Number", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Beta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Alpha Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Alpha Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_Event_Number", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```

#### Alpha Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_Event_Duration", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```

#### Theta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```

#### Theta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Number", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```

#### Theta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Duration", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```

### Latency
#### Gamma Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma_log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```
#### Gamma Event Number

```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma_Event_Number", "mgsLatency") #define what you want in the mediation analysis

MediationAnalysisFixation(other_vars)

```

#### Gamma Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Gamma_Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Beta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Beta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_Event_Number", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Beta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Alpha Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysisFixation(other_vars)

```

#### Alpha Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_Event_Number", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```

#### Alpha Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_Event_Duration", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```

#### Theta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```
#### Theta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Number", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```

#### Theta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Duration", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysisFixation(other_vars)

```

# Mediation Analysis: Trial Level using Inverse Age 
## Delay Period
### Position Error
#### Gamma Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma_log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Gamma Event Number

```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma_Event_Number", "absPositionError") #define what you want in the mediation analysis

MediationAnalysis_inverseAge(other_vars)

```


#### Gamma Event Number and power 

```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma_Event_Number", "Gamma_log1p_Trial_Power") #define what you want in the mediation analysis

MediationAnalysis_inverseAge(other_vars)

```

#### Gamma Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Gamma_Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Beta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```
#### Beta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_Event_Number", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Beta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Alpha Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Alpha Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_Event_Number", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```

#### Alpha Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_Event_Duration", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```

#### Theta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```

#### Theta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Number", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```

#### Theta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Duration", "absPositionError") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```

### Latency
#### Gamma Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma_log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```
#### Gamma Event Number

```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma_Event_Number", "mgsLatency") #define what you want in the mediation analysis

MediationAnalysis_inverseAge(other_vars)

```

#### Gamma Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Gamma_Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Beta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Beta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_Event_Number", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Beta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Beta_Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Alpha Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_inverseAge(other_vars)

```

#### Alpha Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_Event_Number", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```

#### Alpha Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Alpha_Event_Duration", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```

#### Theta Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```
#### Theta Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Number", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```
#### Theta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
other_vars <-c("Theta_Event_Duration", "mgsLatency") #define what you want in the mediation analysis 
MediationAnalysis_inverseAge(other_vars)

```



# Mediation Analysis: Subject Level 
## Delay Period
### Position Error

#### Gamma Trial Power 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")

alldf <- DelayOnly_Sublevel()
alldata_delayOnly <- alldf$alldata_delayOnly

other_vars <-c("Gamma.log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```


#### Gamma Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma.log1p_Trial_Power_Variability", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Gamma Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma.Event_Number_Variability", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Gamma Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma.Event_Number_Variability", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Gamma Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma.Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Gamma Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma.Event_Duration_Variability", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Beta Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Beta.log1p_Trial_Power_Variability", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Beta Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Beta.Event_Number_Variability", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Beta Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Beta.Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```
#### Alpha Trial Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Alpha.log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```
#### Alpha Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Alpha.log1p_Trial_Power_Variability", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```
#### Alpha Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Alpha.Event_Number", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Alpha Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Alpha.Event_Duration", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```
### Latency
#### Gamma Trial Power 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")

alldf <- DelayOnly_Sublevel()
alldata_delayOnly <- alldf$alldata_delayOnly

other_vars <-c("Gamma.log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```


#### Gamma Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma.log1p_Trial_Power_Variability", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Gamma Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma.Event_Number", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Gamma Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma.Event_Number_Variability", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Gamma Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma.Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Gamma Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Gamma.Event_Duration_Variability", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

 ```



## Resting State 
### Position Error
#### Gamma Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")


alldf_RS <- Resting_State_Data_TrialLevel()
alldata_RS_TrialLevel <- alldf_RS$alldata_RS_TrialLevel

other_vars <-c("Gamma.log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_RestingState(alldata_RS_TrialLevel, other_vars)

```

##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf_RS <- Resting_State_Data_TrialLevel()
alldata_RS_TrialLevel <- alldf_RS$alldata_RS_TrialLevel

alldata_RS_TrialLevel_youngest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 1,]
alldata_RS_TrialLevel_Secondyoungest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 2,]
alldata_RS_TrialLevel_thirdyoungest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 3,]
alldata_RS_TrialLevel_oldest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 4,]

other_vars <-c("Gamma.log1p_Trial_Power", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_RestingState(alldata_RS_TrialLevel_youngest, other_vars)



```

#### Gamma Event Number

```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma.Event_Number", "absPositionError") #define what you want in the mediation analysis

MediationAnalysis_RestingState(alldata_RS_TrialLevel, other_vars)
```

##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf_RS <- Resting_State_Data_TrialLevel()
alldata_RS_TrialLevel <- alldf_RS$alldata_RS_TrialLevel

alldata_RS_TrialLevel_youngest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 1,]
alldata_RS_TrialLevel_Secondyoungest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 2,]
alldata_RS_TrialLevel_thirdyoungest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 3,]
alldata_RS_TrialLevel_oldest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 4,]

other_vars <-c("Gamma.Event_Number", "absPositionError") #define what you want in the mediation analysis 

MediationAnalysis_RestingState(alldata_RS_TrialLevel_oldest, other_vars)



```
#### Beta Event Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Beta.Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```
#### Alpha Trial Power 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")

alldf <- DelayOnly_Sublevel()
alldata_delayOnly <- alldf$alldata_delayOnly

other_vars <-c("Alpha.log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```
#### Alpha Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")

alldf <- DelayOnly_Sublevel()
alldata_delayOnly <- alldf$alldata_delayOnly

other_vars <-c("Alpha.log1p_Trial_Power_Variability", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```
#### Alpha Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")

alldf <- DelayOnly_Sublevel()
alldata_delayOnly <- alldf$alldata_delayOnly

other_vars <-c("Alpha.Event_Number", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```

#### Alpha Duration
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")

alldf <- DelayOnly_Sublevel()
alldata_delayOnly <- alldf$alldata_delayOnly

other_vars <-c("Alpha.Event_Duration", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel(alldata_delayOnly, other_vars)

```
### Latency 
#### Gamma Power
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/01.PrepData.R")


alldf_RS <- Resting_State_Data_TrialLevel()
alldata_RS_TrialLevel <- alldf_RS$alldata_RS_TrialLevel

other_vars <-c("Gamma.log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_RestingState(alldata_RS_TrialLevel, other_vars)

```

##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf_RS <- Resting_State_Data_TrialLevel()
alldata_RS_TrialLevel <- alldf_RS$alldata_RS_TrialLevel

alldata_RS_TrialLevel_youngest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 1,]
alldata_RS_TrialLevel_Secondyoungest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 2,]
alldata_RS_TrialLevel_thirdyoungest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 3,]
alldata_RS_TrialLevel_oldest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 4,]

other_vars <-c("Gamma.log1p_Trial_Power", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_RestingState(alldata_RS_TrialLevel_oldest, other_vars)



```

#### Gamma Event Number
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

other_vars <-c("Gamma.Event_Number", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_RestingState(alldata_RS_TrialLevel, other_vars)

```


##### Separate Age Groups 
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}

alldf_RS <- Resting_State_Data_TrialLevel()
alldata_RS_TrialLevel <- alldf_RS$alldata_RS_TrialLevel

alldata_RS_TrialLevel_youngest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 1,]
alldata_RS_TrialLevel_Secondyoungest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 2,]
alldata_RS_TrialLevel_thirdyoungest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 3,]
alldata_RS_TrialLevel_oldest <- alldata_RS_TrialLevel[alldata_RS_TrialLevel$Group == 4,]

other_vars <-c("Gamma.Event_Number", "mgsLatency") #define what you want in the mediation analysis 

MediationAnalysis_RestingState(alldata_RS_TrialLevel_oldest, other_vars)



```

## Fixation Period
### Position Error
#### Gamma Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("log1p_Trial_Power_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_GammaFix(other_vars)

```


#### Gamma Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Number_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_GammaFix(other_vars)

```

#### Gamma Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Duration_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_GammaFix(other_vars)

```

#### Beta Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("log1p_Trial_Power_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_BetaFix(other_vars)

```

#### Beta Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Number_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_BetaFix(other_vars)

```

#### Beta Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Duration_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_BetaFix(other_vars)

```


#### Alpha Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("log1p_Trial_Power_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_AlphaFix(other_vars)

```

#### Alpha Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Number_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_AlphaFix(other_vars)

```

#### Alpha Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Duration_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_AlphaFix(other_vars)

```


#### Theta Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("log1p_Trial_Power_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_ThetaFix(other_vars)

```

#### Theta Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Number_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_ThetaFix(other_vars)

```

#### Theta Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Duration_Variability_Fix", "absPositionError_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_ThetaFix(other_vars)

```


### Latency
#### Gamma Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("log1p_Trial_Power_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_GammaFix(other_vars)

```


#### Gamma Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Number_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_GammaFix(other_vars)

```

#### Gamma Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Duration_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_GammaFix(other_vars)

```

#### Beta Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("log1p_Trial_Power_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_BetaFix(other_vars)

```

#### Beta Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Number_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_BetaFix(other_vars)

```

#### Beta Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Duration_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_BetaFix(other_vars)

```


#### Alpha Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("log1p_Trial_Power_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_AlphaFix(other_vars)

```

#### Alpha Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Number_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_AlphaFix(other_vars)

```

#### Alpha Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Duration_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_AlphaFix(other_vars)

```


#### Theta Trial Power Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("log1p_Trial_Power_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_ThetaFix(other_vars)

```

#### Theta Event Number Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Number_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_ThetaFix(other_vars)

```

#### Theta Event Duration Variability
```{r, echo= FALSE, message = FALSE, warning = FALSE, fig.keep='all'}
source("H:/Projects/7TBrainMech/scripts/eeg/Shane/Rscripts/05.MediationAnalysis.R")

other_vars <-c("Event_Duration_Variability_Fix", "mgsLatency_Variability") #define what you want in the mediation analysis 

MediationAnalysis_SubjectLevel_ThetaFix(other_vars)

```


